ZCB Pricing

### 2018-08-05 Draft.tex
Update Draft.tex

	\begin{tabular}{|>{\centering\arraybackslash}m{4.5cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2.5cm}|}
		\hline
		Numerical Method & Price & Known Price & Error & Computation Time \\ 
		\hline
		Crude Monte Carlo & 0.62136 & 0.62164 & 0.00028 & 1.41000 & 0.37700\\ 
		Antithetic Variates & 0.62826 & 0.62164 & -0.00662 & 1.89000 & 0.10100\\ 
		Moment Matching & 0.62823 & 0.62164 & -0.00659 & 0.89000 & 0.09700\\ 
		Control Variates & 0.62244 & 0.62164 & -0.00081 & 2.75000 & 0.59300\\ 
		Explicit Method & 0.62194 & 0.62164 & -0.00031 & 0.11000 & 0.08400\\ 
		Implicit Method & 0.62193 & 0.62164 & -0.00030 & 0.14000 & 0.11300\\ 
		Crank-Nicolson Method & 0.62188 & 0.62164 & -0.00024 & 0.23000 & 0.15900\\  
		\hline
	\end{tabular}
\end{table}
newpage
\subsection{Sensitivity tests}
\label{subsec: Senses}
In order to confirm that the behaviour of the numerical methods is as expected under different parameters, several different parameter values are tested. The initial set of parameters are those used in section \ref{sec : Compar}. From here the input parameters are varied one at time, with $\alpha$ and $\beta$ varied together in the final two scenarios tested. For each parameter varied, the bond price produced by each numerical method (labelled from 2 to 8 in the order Closed Form,Crude Monte Carlo, Antithetic Variates, Moment Matching, Control Variates, Explicit, Implicit, Crank Nicholson) under the chosen scenarios is plotted along with the bond price produced by the closed form solution (labelled 1).\\\\
In varying the interest rate from the initial $8\%$, all methods behave as expected. When the interest rate is reduced to $5\%$, the bond price decreases. When the interest rate is raised to $10\%$, the bond price increases.	Varying the time to maturity ($T$) from the initial $5$ years also results in the expected behaviour: bond prices increase when $T=1$ and decrease when $T=10$. However, the bond price produced by the explicit method decreases significantly and is in fact $-4.873359\times10^{32}$. This is caused by [missing].\\\\
All the methods don't result in significant changes to the bond price when the standard deviation is increases from the initial $0.5\%$ to $1\%$. When the standard deviation decreases to $0.1\%$, the Monte-Carlo methods don't see significant changes in bond prices while the finite differences produce bond prices in excess of 2. This highlights the flaw in finite difference methods in that they produce very large prices, that don't make financial sense since they exceed the pay-off of the bond, when the standard deviation is sufficiently small and almost vanishes from the PDE along with its coefficients.\\\\
When alpha is decreased from the initial $0.08$, the bond prices for all methods increase. When alpha is increased, the bond prices for all methods decrease, with the price produced by the explicit method again decreasing rapidly to $-1.257679$. When the value of beta is decreased from the initial $0.8$, the bond price produced by all methods decreases. When beta is increases, the bond price produced by all methods increases, which the exception of the explicit. For the explicit method, the price is once again negative and equal to $-2.492100\times10^{45}$. If alpha and beta are varied simultaneously such the mean remains constant and only the mean reversion rate changes then the bond prices don't vary significantly, with the prices being higher for the higher mean reversion rates (i.e. the higher beta value). Again an exception is found with the explicit method, where the price for the increased beta is $-5.065734\times10^{34}$.
	\newpage
	\section{Discussion}
	\label{sec: Discuss}

>>>>

	\begin{tabular}{|>{\centering\arraybackslash}m{4.5cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2cm}|>{\centering\arraybackslash}m{2.5cm}|>{\centering\arraybackslash}m{2.5cm}|}
		\hline
		Numerical Method & Price & Known Price & Error & Computation Time & Computation Time \\ 
		\hline
		Crude Monte Carlo & 0.62136 & 0.62164 & 0.00028 & 1.41000 & 0.37700\\ 
		Antithetic Variates & 0.62826 & 0.62164 & -0.00662 & 1.89000 & 0.10100\\ 
		Moment Matching & 0.62823 & 0.62164 & -0.00659 & 0.89000 & 0.09700\\ 
		Control Variates & 0.62244 & 0.62164 & -0.00081 & 2.75000 & 0.59300\\ 
		Explicit Method & 0.62194 & 0.62164 & -0.00031 & 0.11000 & 0.08400\\ 
		Implicit Method & 0.62193 & 0.62164 & -0.00030 & 0.14000 & 0.11300\\ 
		Crank-Nicolson Method & 0.62188 & 0.62164 & -0.00024 & 0.23000 & 0.15900\\  
		\hline
	\end{tabular}
\end{table}
newpage
\subsection{Sensitivity tests}
\label{subsec: Senses}
In order to confirm that the behaviour of the numerical methods is as expected under different parameters, several different parameter values are tested. The initial set of parameters are those used in section \ref{sec : Compar}. From here the input parameters are varied one at time, with $\alpha$ and $\beta$ varied together in the final two scenarios tested. For each parameter varied, the bond price produced by each numerical method (labelled from 2 to 8 in the order Closed Form,Crude Monte Carlo, Antithetic Variates, Moment Matching, Control Variates, Explicit, Implicit, Crank Nicholson) under the chosen scenarios is plotted along with the bond price produced by the closed form solution (labelled 1).\\\\
In varying the interest rate from the initial $8\%$, all methods behave as expected. When the interest rate is reduced to $5\%$, the bond price decreases. When the interest rate is raised to $10\%$, the bond price increases.	Varying the time to maturity ($T$) from the initial $5$ years also results in the expected behaviour: bond prices increase when $T=1$ and decrease when $T=10$. However, the bond price produced by the explicit method decreases significantly and is in fact $-4.873359\times10^{32}$. This is caused by [missing].\\\\
All the methods don't result in significant changes to the bond price when the standard deviation is increases from the initial $0.5\%$ to $1\%$. When the standard deviation decreases to $0.1\%$, the Monte-Carlo methods don't see significant changes in bond prices while the finite differences produce bond prices in excess of 2. This highlights the flaw in finite difference methods in that they produce very large prices, that don't make financial sense since they exceed the pay-off of the bond, when the standard deviation is sufficiently small and almost vanishes from the PDE along with its coefficients.\\\\
When alpha is decreased from the initial $0.08$, the bond prices for all methods increase. When alpha is increased, the bond prices for all methods decrease, with the price produced by the explicit method again decreasing rapidly to $-1.257679$. When the value of beta is decreased from the initial $0.8$, the bond price produced by all methods decreases. When beta is increases, the bond price produced by all methods increases, which the exception of the explicit. For the explicit method, the price is once again negative and equal to $-2.492100\times10^{45}$. If alpha and beta are varied simultaneously such the mean remains constant and only the mean reversion rate changes then the bond prices don't vary significantly, with the prices being higher for the higher mean reversion rates (i.e. the higher beta value). Again an exception is found with the explicit method, where the price for the increased beta is $-5.065734\times10^{34}$.
	\newpage
	\section{Discussion}
	\label{sec: Discuss}
